Tables

### 2019-07-15 code/tables.rmd
Clarifications of some effect descriptions Table 2

description <- c("Two correlational effects: 'Gender math attitude' compared implicit attitudes (IAT) towards math between genders and 'IAT correlation math' correlated implicit attitudes with self-reported measures. The remainder were experiments with two independent groups. The groups were primed in some way (Anchoring 1-4; low vs. high category scales; norm of reciprocity; flag priming; currency priming), asked to imagine slightly different situations (Sunk costs; gain vs. loss framing; gambler's fallacy; imagined contact) or asked their agreement with statements presented differently (Allowed vs. forbidden; quote attribution). ", #ML1
            "Several effects were experiments with two independent groups. The groups were either primed in some way (Power and perspective; warmth perceptions; subjective distance interaction), saw slightly different statements (Elaboration likelihood interaction; credentials interaction) or experienced different situations (weight embodiment). Examined interactions were between treatment conditions and participant characteristics. One priming effect (metaphor) compared two treatment groups with a control. One effect was correlational: 'persistence and conscientiousness' was measured by an unsolvable anagram task and self-report respectively. The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML2
                 "Verbal overshadowing 1; Independent two-group experiment. Participants either described a robber after watching a video or listed countries/capitals and after a filler task attempted to identify the robber in a lineup.", #RRR1
            "Verbal overshadowing 2; Different from 1 only in that the filler task took place before the descriptive task instead of after.", #RRR2
                 "Grammar on intentionality/intention attribution/detailed processing; Independent two-group experiment with three outcome variables. Actions either described in imperfect or perfect.", #RRR3
            "Ego depletion; Independent two-group experiment. Participants either assigned to a cognitively demanding task or a neutral, and performance was then measured in a subsequent cognitive task.", #RRR4
            "Commitment on neglect/exit; Independent two-group experiment with two outcome variables. Participants either primed to think about commitment to or independence from partner.", #RRR5
            "Facial feedback hypothesis; Independent two-group experiment. Participants either induced to 'smile' or 'pouth' with a pen and then rated funniness of cartoons. ", #RRR6
            "Intuitive cooperation; Independent two-group experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
                 "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.") #RRR8

@@

sample_settings <- c("26/36 samples were primarily university students, 3 general population and 7 undescribed. 9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
                     "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
                     "31/32 samples were undergraduate students between 18-25, 1 general population which was also the only online sample.", #RRR1
                     "22/23 samples were undergraduate students between 18-25, 1 general population which was also the only online sample.", #RRR2
                     "11/12 samples were undergraduate students mostly between 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
                     "All samples consisted of in-lab undergraduate students", #RRR4
                     "All samples consisted of in-lab undergraduate students between 18-25", #RRR5
               "All but one sample explicitly consisted of students and all took place in-lab. The last sample was recruited at university grounds.", #RRR6
               'All samples consisted of in-lab undergraduate students between 18-34.', #RRR7
                     "All samples consisted of in-lab undergraduate students betweeb 18-25") #RRR8

>>>>

description <- c("Two correlational effects: 'Gender math attitude' compared implicit attitudes (IAT) towards math between genders and 'IAT correlation math' correlated implicit attitudes with self-reported measures. The remainder were experiments with two independent groups. The groups were primed in some way (Anchoring 1-4; low vs. high category scales; norm of reciprocity; flag priming; currency priming), asked to imagine slightly different situations (Sunk costs; gain vs. loss framing; gambler's fallacy; imagined contact) or asked their agreement with statements presented differently (Allowed vs. forbidden; quote attribution). ", #ML1
            "Several effects were experiments with two independent groups. The groups were either primed in some way (Power and perspective; warmth perceptions; subjective distance interaction), saw slightly different statements (Elaboration likelihood interaction; credentials interaction) or experienced different situations (weight embodiment). Examined interactions were between treatment conditions and participant characteristics. One priming effect (metaphor) compared two treatment groups with a control. One effect was correlational: 'persistence and conscientiousness' was measured by an unsolvable anagram task and self-report respectively. The Stroop task is a within-person experiment with two conditions and the 'Availability' effect asks participants to judge whether some letters are more common in the first or third position.", #ML2
                 "Verbal overshadowing 1; Independent two-group experiment. Participants either described a robber after watching a video or listed countries/capitals and after a filler task attempted to identify the robber in a lineup.", #RRR1
            "Verbal overshadowing 2; Different from 1 only in that the filler task took place before the descriptive task instead of after.", #RRR2
                 "Grammar's effect on interpretation; Independent two-group vignette experiment with three outcome variables. Participants read about actions either described in imperfect or perfect tense and then rated protagonist's intentions (intentionality/intention attribution/detailed processing).", #RRR3
            "Ego depletion; Independent two-group experiment. Participants either assigned to a cognitively demanding task or a neutral, and performance was then measured in a subsequent cognitive task.", #RRR4
            "Commitment on neglect/exit; Independent two-group experiment with two outcome variables. Participants either primed to think about commitment to or independence from partner.", #RRR5
            "Facial feedback hypothesis; Independent two-group experiment. Participants either induced to 'smile' or 'pouth' by holding a pen in their mouth differently and simultaneously rated funniness of cartoons. ", #RRR6
            "Intuitive cooperation; Independent two-group experiment. Economic game with money contribution to a common pool either under time pressure or time delay.",
                 "Professor priming; Independent two-group experiment. Participants primed with either a 'professor' or 'hooligan' stimuli. Outcome was percentage correct trivia answers.") #RRR8

@@

sample_settings <- c("26/36 samples were primarily university students, 3 general population and 7 undescribed. 9/36 samples were online, including all the general population ones.", #https://osf.io/g3udn/, ML1
                     "20/21 samples were university students, 1 general population which was also the only online sample.", #Ml3
                     "31/32 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR1
                     "22/23 samples were undergraduate students aged 18-25, 1 general population which was also the only online sample.", #RRR2
                     "11/12 samples were undergraduate students mostly aged 18-25, one of which was online. 1 sample was a broader online sample.", #RRR3
                     "All samples consisted of in-lab undergraduate students", #RRR4
                     "All samples consisted of in-lab undergraduate students aged 18-25", #RRR5
               "All but one sample explicitly consisted of students and all took place in-lab. The last sample was recruited at university grounds.", #RRR6
               'All samples consisted of in-lab undergraduate students aged 18-34.', #RRR7
                     "All samples consisted of in-lab undergraduate students aged 18-25") #RRR8
